The supernova-regulated ISM - III. Magnetic fields in the multi-phase gas

### 2015-03-13 paper.tex
Fixed some references

FAG -- notes -- include Beck, Fletcher, Berkhuijsen observations of magnetic 
fields \citep{2013AN....334..548B, MNR18065} and observation/estimates of multiphase structure \citep{dummy}
\citep{CS74,M077}

@@

%FAG rephrase
The decomposition of the magnetic field into mean and fluctuating (random) 
field follows \MHD.
%end FAG
%When considering the mean-field decomposition of the magnetic field, the notation used by \citep{GSSFM13} is adopted.
Volume averaging with a Gaussian kernel, $G_{l}(\bvec{x}-\bvec{x}')$ is used to decompose the magnetic field, $\bvec{B}$, into mean (large-scale), $\bvec{B}_{l}$ and random (small-scale), $\bvec{b}_{l}$, fields. The decomposition is given by 
\begin{equation}
\bvec{B} = \bvec{B}_{l}+\bvec{b}_{l},\qquad \bvec{B}_{l} = \avg{B}. \label{decomp} 
\end{equation}
Gaussian smoothing of the magnetic field with kernel size $l$ is represented by
\begin{align}
\avg{B}&=\int_{V}\bvec{B}(\bvec{x}')G_{l}(\bvec{x}-\bvec{x}')d^{3}\bvec{x}',\\
G_{l}(\bvec{x})&=(2\pi l^2)^{-3/2}\exp[-\bvec{x}/(2l^2)],\nonumber
\label{gauss}
\end{align} 
where $l\approx50$pc is half the integral scale of random motions \citep{GSSFM13}. This value is adopted for this paper based on the justification given in \citep{gent2}.  Preliminary analysis does not show significant sensitivity of the mean or random field to variations in $l$ within the range $0<l<100$pc. However, future work will consider analysis of isolated structures in the ISM. A more detailed analysis of length and correlation scales will be carried out. However, the current definition, $l=50$pc, is sufficient for the purposes of this paper. 
%\begin{table*}
 %\centering
 %\begin{minipage}{140mm}
  %\caption{Data on the RV Tauri stars detected by {\it IRAS}.}
  %\begin{tabular}{@{}llrrrrlrlr@{}}
  %\hline
  % Name     &            & \multicolumn{4}{c}{Flux density (Jy)%
 %\footnote{Observed by {\em IRAS}.}}\\
 % Variable & {\it IRAS} & 12$\,\umu$m & 25$\,\umu$m & 60$\,\umu$m
 %    & 100$\,\umu$m & Sp. & Period & Light- & $T_0\,(\rmn{K})$ \\
 %       &  &  &  &  &  & group & (d) & curve \\
 %       &  &  &  &  &  &       &     & type  \\
 %\hline
 %TW Cam & 04166$+$5719 & 8.27 & 5.62 & 1.82 & $<$1.73 & A & 85.6 & a & 555 \\
 %RV Tau & 04440$+$2605 & 22.53 & 18.08 & 6.40 & 2.52 & A & 78.9 & b & 460 \\
%\hline
%\end{tabular}
%\end{minipage}
%\end{table*}

@@

Magnetic field lines give a qualitative description of the magnetic field in 
the ISM. 
We introduce sampling of physical variables along the field lines of the 
magnetic field, to obtain a quantitative description of the observables. 
Observables, such as entropy or pulsar RM measures \citep{SSFS02} are 
frequently used to derive other observables or statistics.  
The use of sampling along field lines will enable the analysis of observables 
across many snapshots, whilst avoiding the use of time averages, which is not 
sensible for observables associated to a turbulent flow \citep{TL72}. 
For example, wavelet transform methods are used by \citet{st02}, to derive the
Galactic magnetic field from pulsar RM data. 
Field lines of the Galactic magnetic field can be derived from this analysis 
and it can be further analysed using sampling along the field lines.

@@

%%\noindent 
%We observe a sharp peak for the PDF of entropy along the field line, centred at $s\approx27\cdot10^8$ erg g$^{-1}$ K$^{-1}$, which is inside the hot phase. A similar peak is not observed for the PDF of entropy along the straight line. This can be explained by the field lines being stretched by the hot gas and thus traversing the hot phase for a higher proportion of their length than the straight lines, which are not affected by stretching. We formulate probabilities of traversing each phase for the field lines and straight lines from their PDFs. The probabilities are expressed as,
%\begin{align}
%\mathcal P(\text{cold phase})&\equiv\mathcal P(s\leq3.7\cdot10^8),\nonumber\\
%\mathcal P(\text{warm phase})&\equiv\mathcal P(3.7\cdot10^8<s<23.2\cdot10^8),\\
%\mathcal P(\text{hot phase})&\equiv\mathcal P(s>23.2\cdot10^8).\nonumber
%\end{align}
%The probabilities of traversing the phases, for the field lines and straight lines, are given in \ref{table:mean_probs}. We observe that the probabilities of the straight lines traversing each phase closely match the fractional volumes of the phases, as expected; lines that are not sensitive should traverse each phase with probability proportional to the fractional volume. 
%On the other hand, the probability of a field line traversing the hot phase is significantly higher than that of a straight line, which reiterates the effect of the stretching of field lines by the phase. The probability of a field line traversing the warm phase is lower than that of a straight line. However, this is a direct consequence of the distortion of the magnetic field by the hot phase. We note that the probability of a field line traversing the cold phase is lower than that of a straight line by an order of magnitude. This could constitute a preliminary indication that the field lines avoid the cold phase. As noted earlier, the characteristics of the magnetic field in the cold phase will be explored in greater detail elsewhere.  
%
%%-----------------------------------------------------------------------------
%\subsection{Field lines of the total and random magnetic field}
%%-----------------------------------------------------------------------------
%
%We use Equation \eqref{f_lines_eqn} to construct field lines for the total and random magnetic field using the same method as for field lines of the mean magnetic field. Sampling along these lines is used to obtain the PDF of  entropy, as seen in the previous section for the mean magnetic field. PDFs of log density and log temperature have been omitted, since the PDF of entropy contains sufficient detail to understand the characteristics of the field lines. The comparison with PDFs along straight lines are only relevant for field lines of the mean magnetic field. This section focuses on the comparison of PDFs along the total, mean and random magnetic field.

%%-----------------------------------------------------------------------------
%\begin{figure}
%\includegraphics[width=\linewidth]{decomp_pdf_overall.pdf}
%\caption{PDFs of $s$ along field lines of the mean (blue solid), total (red solid) and random (green solid) fields. The boundaries of between the cold and warm phases (black dashed) and between the warm and hot phases (black solid) are indicated.}
%\label{fig:tot_pdfs}
%\end{figure}
%%-----------------------------------------------------------------------------

>>>>

FAG -- notes -- include Beck, Fletcher, Berkhuijsen observations of magnetic 
fields \citep{2013AN....334..548B, MNR18065} and observation/estimates of multiphase structure 
\citep{CS74,MO77}

@@

%FAG rephrase
The decomposition of the magnetic field into mean and fluctuating (random) 
field follows \MHD.
%end FAG
%When considering the mean-field decomposition of the magnetic field, the notation used by \citep{GSSFM13} is adopted.
Volume averaging with a Gaussian kernel, $G_{l}(\bvec{x}-\bvec{x}')$ is used to decompose the magnetic field, $\bvec{B}$, into mean (large-scale), $\bvec{B}_{l}$ and random (small-scale), $\bvec{b}_{l}$, fields. The decomposition is given by 
\begin{equation}
\bvec{B} = \bvec{B}_{l}+\bvec{b}_{l},\qquad \bvec{B}_{l} = \avg{B}. \label{decomp} 
\end{equation}
Gaussian smoothing of the magnetic field with kernel size $l$ is represented by
\begin{align}
\avg{B}&=\int_{V}\bvec{B}(\bvec{x}')G_{l}(\bvec{x}-\bvec{x}')d^{3}\bvec{x}',\\
G_{l}(\bvec{x})&=(2\pi l^2)^{-3/2}\exp[-\bvec{x}/(2l^2)],\nonumber
\label{gauss}
\end{align} 
where $l\approx50$pc is half the integral scale of random motions, as discussed
in \HD.  
reliminary analysis does not show significant sensitivity of the mean or random field to variations in $l$ within the range $0<l<100$pc. However, future work will consider analysis of isolated structures in the ISM. A more detailed analysis of length and correlation scales will be carried out. However, the current definition, $l=50$pc, is sufficient for the purposes of this paper. 
%\begin{table*}
 %\centering
 %\begin{minipage}{140mm}
  %\caption{Data on the RV Tauri stars detected by {\it IRAS}.}
  %\begin{tabular}{@{}llrrrrlrlr@{}}
  %\hline
  % Name     &            & \multicolumn{4}{c}{Flux density (Jy)%
 %\footnote{Observed by {\em IRAS}.}}\\
 % Variable & {\it IRAS} & 12$\,\umu$m & 25$\,\umu$m & 60$\,\umu$m
 %    & 100$\,\umu$m & Sp. & Period & Light- & $T_0\,(\rmn{K})$ \\
 %       &  &  &  &  &  & group & (d) & curve \\
 %       &  &  &  &  &  &       &     & type  \\
 %\hline
 %TW Cam & 04166$+$5719 & 8.27 & 5.62 & 1.82 & $<$1.73 & A & 85.6 & a & 555 \\
 %RV Tau & 04440$+$2605 & 22.53 & 18.08 & 6.40 & 2.52 & A & 78.9 & b & 460 \\
%\hline
%\end{tabular}
%\end{minipage}
%\end{table*}

@@

Magnetic field lines give a qualitative description of the magnetic field in 
the ISM. 
We introduce sampling of physical variables along the field lines of the 
magnetic field, to obtain a quantitative description of the observables. 
Observables, such as entropy or pulsar RM measures \citep{SFSS02} are 
frequently used to derive other observables or statistics.  
The use of sampling along field lines will enable the analysis of observables 
across many snapshots, whilst avoiding the use of time averages, which is not 
sensible for observables associated to a turbulent flow \citep{TL72}. 
For example, wavelet transform methods are used by \citet{SFSS02}, to derive the
Galactic magnetic field from pulsar RM data. 
Field lines of the Galactic magnetic field can be derived from this analysis 
and it can be further analysed using sampling along the field lines.

@@

%%\noindent 
%We observe a sharp peak for the PDF of entropy along the field line, centred at $s\approx27\cdot10^8$ erg g$^{-1}$ K$^{-1}$, which is inside the hot phase. A similar peak is not observed for the PDF of entropy along the straight line. This can be explained by the field lines being stretched by the hot gas and thus traversing the hot phase for a higher proportion of their length than the straight lines, which are not affected by stretching. We formulate probabilities of traversing each phase for the field lines and straight lines from their PDFs. The probabilities are expressed as,
%\begin{align}
%\mathcal P(\text{cold phase})&\equiv\mathcal P(s\leq3.7\cdot10^8),\nonumber\\
%\mathcal P(\text{warm phase})&\equiv\mathcal P(3.7\cdot10^8<s<23.2\cdot10^8),\\
%\mathcal P(\text{hot phase})&\equiv\mathcal P(s>23.2\cdot10^8).\nonumber
%\end{align}
%The probabilities of traversing the phases, for the field lines and straight lines, are given in \ref{table:mean_probs}. We observe that the probabilities of the straight lines traversing each phase closely match the fractional volumes of the phases, as expected; lines that are not sensitive should traverse each phase with probability proportional to the fractional volume. 
%On the other hand, the probability of a field line traversing the hot phase is significantly higher than that of a straight line, which reiterates the effect of the stretching of field lines by the phase. The probability of a field line traversing the warm phase is lower than that of a straight line. However, this is a direct consequence of the distortion of the magnetic field by the hot phase. We note that the probability of a field line traversing the cold phase is lower than that of a straight line by an order of magnitude. This could constitute a preliminary indication that the field lines avoid the cold phase. As noted earlier, the characteristics of the magnetic field in the cold phase will be explored in greater detail elsewhere.  
%
%%-----------------------------------------------------------------------------
%-----------------------------------------------------------------------------
%\subsection{Field lines of the total and random magnetic field}
%%-----------------------------------------------------------------------------
%
%We use Equation \eqref{f_lines_eqn} to construct field lines for the total and random magnetic field using the same method as for field lines of the mean magnetic field. Sampling along these lines is used to obtain the PDF of  entropy, as seen in the previous section for the mean magnetic field. PDFs of log density and log temperature have been omitted, since the PDF of entropy contains sufficient detail to understand the characteristics of the field lines. The comparison with PDFs along straight lines are only relevant for field lines of the mean magnetic field. This section focuses on the comparison of PDFs along the total, mean and random magnetic field.

%%-----------------------------------------------------------------------------
%\begin{figure}
%\includegraphics[width=\linewidth]{decomp_pdf_overall.pdf}
%\caption{PDFs of $s$ along field lines of the mean (blue solid), total (red solid) and random (green solid) fields. The boundaries of between the cold and warm phases (black dashed) and between the warm and hot phases (black solid) are indicated.}
%\label{fig:tot_pdfs}
%-----------------------------------------------------------------------------
%\end{figure}
%%-----------------------------------------------------------------------------
